Benchmarking neuromorphic systems with Nengo

### 2015-09-14 paper/rebuttals.txt

> The materials and methods describes well the metrics and models used
> to evaluate the backends.

4. Other comments on the results.
---------------------------------

> 1. Further clarification should be given as to why the SpiNNaker
> backend was not tested for compliance, as lines 276-77 are not
> sufficient. The reason is not clear as build and run time for the
> examined models in Figures 5-7 do not seem prohibitive to running
> 212 tests; additionally, SpiNNaker supports a wide variety of neuron
> models and parameters, so it appears adequate to support the
> necessary descriptions required by Nengo. Please clarify.

You are completely correct that this comment is not sufficient.
A technical answer would be that SpiNNaker has a lot of
set up and tear down code, which makes running the test suite
slow and error-prone. The tests creates a large number of
small models and run them for small amounts of time;
this results in the SpiNNaker boards' memory filling up with
improperly freed resources. The real answer is a matter of
time management; we decided that getting the unit tests
running would take too much time for this paper.
However, this answer is not very satisfying, so we have
put in the time to run the test suite with the SpiNNaker
backend. Table 1 (Table 2 in the revised version) now gives results
for the SpiNNaker backend, and the text has been updated
accordingly.

@@

> 2. Lines 320-325 are not clear.

> a) While Figure 6 does show an increase for the Nengo reference
> backend run times by removing passthrough nodes, the run time appears
> to be a 15% increase (~7x vs ~6x slower than real-time, Figure 6
> green, BG Sequence to BG Sequence *), which is approximately the same
> relative speedup as that offered by removing probes for the SpiNNaker
> backend (~1.5x to ~1.2x, Figures 6 and 7, BG sequence, blue). So,
> "significant" is a strong claim and should be clarified.

Good point. We used 'significant' colloquially here and
have therefore reworded the paragraph; it now reads:

@@

> b) Additionally, Figure 7 seems to indicate that removing probes
> actually makes the network slower for the reference backend for BG
> sequence * (~8x vs ~6.8x, Figures 6 and 7, light blue, BG Sequence
> *). Either outliers / standard deviations are stronger than they
> appear from the plot, or the reason for the network slowing down with
> probes removed should be explained.

We did not notice the slowdown upon initial submission,
so seeing this was puzzling to us as well.
To investigate whether this effect was real,
we first replicated it on two additional machines;
the version without probes was significantly slower
than the version with probes on all machines,
as measured by non-overlapping
bootstrapped 95% confidence intervals.
Then, we investigated the internal structures of the two
versions of networks, in terms of the step functions
produced by them.
The version with probes had 600 step functions;
595 of these implemented the same equations
as the networks without probes, while the
remaining five functions implemented the probing.
The simulator loop also indicated that
the version without probes should have executed
strictly fewer operations than the version with probes.
We conclude that the reason for the speedup
must have been somehow related to
a lower level of abstraction than we investigated
(e.g., the data was better organized in RAM
in the version with probes).

Very few networks in Nengo have zero probes,
so there were some obvious opportunities to optimize
the reference backend for the special case
in which no probes exist. After implementing
two such optimizations, we were able to consistently
achieve identical performance with probes and without.
However, it was not our intention to perform
a detailed comparison of the effect of probes
on runtimes, and we feel that including Figure 7
(which only had a few sentences of text associated with it)
was more distracting than illuminating.
For these reasons, we have removed Figure 7 in this revision.

@@

We have verified that the error bars reported are bootstrapped 95%
confidence intervals, as claimed in the figure captions of
Figures 5 and 6. As previously mentioned, we also replicated
the paradoxical slowdown with probes removed; however,
with the removal of Figure 7, we believe that additional text attesting
to the validity of the confidence intervals is not warranted.

> 3. In Figure 3, the meaning of negative frequencies (-1 Hz, -2 Hz)
> should be at least briefly mentioned. Presumably, since this is a
> circular oscillator, it is being run in reverse. However, it's not
> clear to me why negative frequencies should be at all different than
> positive frequencies, and how the range -2 Hz to 2 Hz was chosen. A
> citation that references this range in biology for CPGs, for example,
> would bolster this choice.

The meaning of negative frequencies has been made explicit in text;
line 239 now notes that "negative frequencies indicate
oscillations in the reverse direction." In that line, we have
also added a footnote with a citation to Duysens and Van de Crommert, 1998,
which provides some evidence that locomotive CPGs may run in reverse
for backward locomotion.

We chose the range of -2 to 2
because we have used oscillators of these frequencies
in previous models. In line 219 we note that
"We test each model with parameters typically used
in large-scale models, but make these parameterized models
available ... for those who wish to explore additional cases."
The parameter is trivial to change, up to an upper frequency limit
which depends on the properties of the neurons in use;
we would be happy to show results for a different set of frequencies
if that would be preferable.

@@

> 4. Table 1, the compliance of the four backends, should be explained
> more fully in the caption. The levels of coverage are surprisingly low
> given that all backends are able to perform the main cognitive-level
> tasks; common failure cases (e.g., missing neuron models) should be
> mentioned to show why these are not necessary.

The caption for the compliance table (which now includes all 5 backends)
has been updated. It now reads:

  Compliance of the five backends. Compliance is the number of
  functional tests passed by a particular backend. We have divided
  these tests into tests parameterized by neuron type, and those not
  parameterized.  Non-parameterized tests are either designed to work
  with only one neuron type, or use leaky integreate-and-fire (LIF)
  neurons, which are implemented on all backends. For parameterized
  tests, we have separated the compliance for those tests using LIF
  neurons, which all backends implement, and for any additional neuron
  types implemented. Since there are 31 parameterized tests, the
  maximum compliance is 31 times the number of neuron types
  implemented.  The reference backend implements three additional
  neuron types, while OpenCL, Distilled, and Brainstorm implement one
  additional neuron type, and SpiNNaker only implements LIF neurons.

Additionally, a paragraph explaining common failure cases
is included in the main text in lines 309-319. It reads:

  It should be noted that these test suites are being run on the
  distilled, Brainstorm, and SpiNNaker backends for the first time in
  this study.  In other words, these results are the first objective
  interrogation of each backend's feature set.  In many cases, tests
  failed by backends are tests of features recently added to Nengo,
  such as stochastic processes for injecting current noise.  As such,
  we expect compliance on all backends to rise quickly as backend
  developers implement these new features.  The OpenCL backend has
  higher compliance in large part because it is developed by the same
  group that develops the reference backend.  However, there are some
  notable features missing from some backends, such as learning
  through plasticity rules applied to neuron-to-neuron connections,
  and implementation differences, such as one timestep delays on
  connections with no synaptic filter, that may remain even when
  backends are brought up to date with the reference implementation.
  It is likely that tests will be rewritten in the future to allow
  some implementation differences if they do not affect simulation
  accuracy.

@@

5. Other comments on the discussion or the conclusions.
-------------------------------------------------------

> The initially stated conclusion that significant speedups can be
> obtained with specialized hardware without sacrificing accuracy is
> good, although perhaps not very surprising. However, the greater
> challenge of creating a list of cognitively-relevant tasks and an
> infrastructure for objective testing is significant. Moreover, the
> improved accuracy of SpiNNaker with passthrough nodes removed,
> discovered by these tests, is an encouraging sign that the
> optimization loop of hardware and implementation through this test
> framework can yield real improvements.
>
> The biggest omission from this discussion and the manuscript is any
> mention of efficiency. Neuromorphic systems have long held that
> their primary advantage is significant efficiency, and the lack of
> ability of the benchmarking to capture that is unfortunate. This
> could perhaps be implemented as an optional query on the backend;
> the power consumption of most CPUs and GPUs can be publicly
> referenced and approximated, or the implementation could provide its
> own statistics for specialized hardware. Perhaps the Brainstorm
> backend’s main advantage is in power efficiency, and there should be
> resulting statistics that can show that. Regardless of
> implementation, the authors should at least mention that efficiency
> could be evaluated in future work.

This is a great point, and indeed points out one of the weaknesses
of the "standardization" approach that we are espousing with Nengo:
new metrics may take a long time to be implemented since they
must be implemented on all backends.

We have a paragraph to the discussion section
to discuss this issue, and to register our desire to collect
efficiency information in future work. Lines 416-422 now read:

  One inherent weakness of using Nengo as a standard platform for
  benchmarking neuromorphic systems is that new benchmarking
  capabilities may take a long time to be standardized and
  developed. If one wishes to add a new metric, such as power
  consumption (as was done in Stromatias et al., 2013), we must first
  come to a consensus on a suitable interface to this information
  through Nengo. Once consensus is reached, it must be implemented and
  tested on all backends before benchmarks can be written using that
  quantity. Despite this limitation, we believe that it is possible to
  use Nengo to collect power consumption information, and plan to
  implement energy efficiency comparisons in future work.

@@

2. Does the introduction present the study in an appropriate context?
---------------------------------------------------------------------

> No

> The introduction gives a clear motivation for the work in the
> article, but it does not state which works have been done previously
> on that topic. For example, there are several articles investigating
> accuracy in neuromorphic hardware for specific benchmark
> problems. As three of the backends are software-based, it would also
> be appropriate here to cite prior work on accuracy/speed in neural
> software simulators.

We have added two paragraphs to the introduction citing prior work
benchmarking SpiNNaker, FACETS, and Brian,
and situating this study in that context on lines 19-35.
They read:

  Prior work benchmarking neural simulators and neuromorphic hardware
  has focused on low-level neural performance.  For example, Sharp and
  Furber (2013) showed that SpiNNaker can simulate a recurrent network
  of leaky integrate-and-fire neurons with similar firing rate and
  inter-spike intervals as the NEST neural simulator, but around six
  times faster.  Stromatias et al. (2013) showed that SpiNNaker's
  power consumption varies between 15 and 37 Watts (0.5--0.8 Watts per
  chip) depending on the number of neurons being simulated.  Goodman
  and Brette (2008) showed that Brian simulated a randomly connected
  network of 4000 leaky integrate-and-fire twice as fast as an
  equivalent Matlab implementation, but around three times slower than
  a C implementation. In all of these cases, none of the networks
  elicited activity that could be directly related to experimentally
  recorded data on a behavioral task.

  In contrast, Ehrlich et al. (2010) and Bruderle et al. (2011) have
  presented a set of benchmarks that target the FACETS neuromorphic
  system through the PyNN Python package.  These benchmarks include an
  attractor-based memory model, a model of self-sustained AI states,
  and a Synfire Chain, all of which are directly related to
  neuroscientific experiments.  We aim to build on this line of
  research to provide an unbiased, efficient, and future-proof set of
  benchmarks that focuses on high-level functional performance using
  Nengo instead of PyNN.  We have previously shown that Nengo is an
  order of magnitude faster than the simulators that PyNN targets
  (Bekolay et al., 2013), and have recently implemented backends that
  target neuromorphic hardware.

@@

3. Other comments on the introduction.
--------------------------------------

> As the Nengo test suite was not designed for benchmarking, it would
> be helpful to have some indications on the limitations of the method
> (its potential is described already pretty clear) - this could be
> done in the Discussion section as well.

We have added a paragraph to the discussion noting that Nengo's
standards-based development and frontend-backend separation mean that
development can be slow (e.g., collecting power consumption
would mean figuring out a standard for this and then implementing
it across all backends) on lines 416-422. It reads:

  One inherent weakness of using Nengo as a standard platform for
  benchmarking neuromorphic systems is that new benchmarking
  capabilities may take a long time to be standardized and
  developed. If one wishes to add a new metric, such as power
  consumption (as was done in Stromatias et al., 2013), we must first
  come to a consensus on a suitable interface to this information
  through Nengo. Once consensus is reached, it must be implemented and
  tested on all backends before benchmarks can be written using that
  quantity. Despite this limitation, we believe that it is possible to
  use Nengo to collect power consumption information, and plan to
  implement energy efficiency comparisons in future work.

@@

4. Other comments on the materials and methods.
-----------------------------------------------

> I found the separation in Background and Methods helpful for
> understanding, even if it does not follow the standard article
> structure. Some points should be clarified:
>
> - The benchmarks make use of current input to neurons. However,
>   quite a lot of neuromorphic systems do only offer spike input, or
>   current inputs are not so flexible to program. Of course, current
>   input can be emulated by spike input, but that may add some
>   additional noise/inaccuracy. This should be dicsussed in the
>   Background/Methods sections; also, an indication on how the
>   currents look like in the benchmark models would be helpful, so
>   that designers of neuromorphic systems get an idea of what would
>   be required.

This is an excellent point that we really should have addressed
in the initial submission. The paper that we cited in the section
on the SpiNNaker backend (Mundy et al., 2015) gives a detailed
account of how SpiNNaker uses decoded values to change the
input currents to individual neurons, and two prior publications
(Galluppi et al., 2012 and Choudhary et al., 2012) describe processes
to implement Nengo with primarily spike-based communication
on SpiNNaker and Neurogrid, respectively.
We have added a paragraph to the Methods section
with brief descriptions of how SpiNNaker handles currents,
and how other neuromorphic hardware can be made to handle
currents from Nengo as well in lines 285-295.
The paragraph reads:

  Unlike software backends, considerable effort is taken to translate
  a Nengo model into something that can run on a SpiNNaker
  board. Fortunately, SpiNNaker can be reprogrammed as it is composed
  of a large collection of chips, each with 18 ARM processing
  cores. Notably, this allows SpiNNaker to take advantage of Nengo’s
  encoding and decoding capabilities, greatly reducing the amount of
  RAM needed (Mundy et al., 2015). The SpiNNaker backend accomplishes
  this by using decoded values to determine changes to the input
  currents of each neuron, rather than using purely spike-based
  transmission. However, neuromorphic hardware that can only
  communicate through spikes can be made to interact with Nengo
  through explicit encoding and decoding processes on the chip, as was
  done in Galluppi et al. (2012), or by using Nengo on the host
  machine to explicitly generate spike patterns that are communicated
  to the device, as was done in Choudhary et al. (2012). However,
  these methods may introduce additional noise in the simulation,
  resulting in inaccuracies.

@@

> - At several points, the authors mention that seeds can be set
>   explicitely for deterministic experiment runs. Is there a reason
>   for this? For benchmarking, setting a fixed seed is misleading in
>   my opinion, as it suggests that all backends run exactly the same
>   experiment. However, as the order in which the single parts of a
>   network are generated is not the same, this is not the case in
>   general. Furthermore, neuromorphic hardware systems may use
>   built-in noise sources (i.e. true random numbers). All that
>   requires a statistical comparison of results over several
>   experiment repetitions, as the authors do in their benchmarks.

Fair point. For logistical reasons, it is often nice to be able
to set a seed and track it; for example, in collecting data for
this paper, each model's results are stored in a file whose name
includes the seed. This makes it easy to ensure that the same
model is not run twice, biasing the sample.
However, in general, it is true that setting seeds is not important
for benchmarking. For this reason, we have removed the mentions
of setting seeds, including references to the `rng` and `seed`
fixtures. We have kept one reference in the Background section discussing
the frontend interface, but have reworded it slightly; it now reads:

@@

  The only parameter on the network is an optional integer seed;
  setting this should make all of the random factors in the model
  deterministic, which is important for testing and debugging models,
  but is not used for benchmarking.

> - The authors state that Nengo is well-suited for generating large
>   networks. However, the tests they present are only limited in
>   size. A comment on larger benchmark models in the test suite
>   and/or the possibility to scale up the present benchmarks would be
>   desirable.

We have added an explicit mention of the size of Spaun on lines 400-401
(since Spaun is built with Nengo and shows that it is possible
to generate large networks). We have also added a short paragraph
to the Test Models subsection discussing larger models;
see lines 255-259 which read:

@@

5. Other comments on the results.
---------------------------------

> I found the description of the Figures on accuracy too short. Even
> if the accuracy results themselves are not the main focus of the
> article, some more explanations for the results should be given. In
> particular, in Figs. 1 and 2, why does the Nengo reference backend
> show a significantly higher variability than the Brainstorm and
> distilled backends? In Figs. 3 and 4, where do the deviations in the
> SpiNNaker backend come from (my first guess would be the employed
> 1ms time step, which is larger than the 0.1ms typically used in
> software simulators)?

We have added additional details in the section 4.2 on accuracy.
These additional details are listed below.

Unfortunately, we do not have a satisfying explanation
for why the reference backend shows higher variability than
the Brainstorm and distilled backends.
We discuss this briefly in the additional details below
and have added a sentence to the discussion
indicating that we will examine this result in the future
(lines 395-397: "We also plan to investigate
why the reference and OpenCL backends
have higher variability than other backends on
the simple feedforward models.")

We are still in the progress of investigating the deviations
in the SpiNNaker backend; however, we are collaborating with
the SpiNNaker group to improve accuracy on these examples.
The 1 ms time step is not the issue here, however,
as all of the backends tested use a 1 ms time step.

@@

Figure 1:

  The Brainstorm and distilled backends have the least variability and
  the SpiNNaker backend has the most variability, though the median
  RSME is the same across all backends.  One driver of these
  differences is in how each backend handles ensembles operating near
  the edge of their representational range (i.e., the radius of the
  ensemble).  The outlier with highest RMSE represents a model
  instance in which the static vector target was at the extreme of the
  representational range; the SpiNNaker backend's relatively high RMSE
  on this example indicates that it may not perform as well as other
  backends in this situation.  The SpiNNaker backend uses signed fixed
  point numbers with 16 digits before the decimal point, and 15 digits
  after the decimal point; accuracy could be improved by optimizing
  the backend's internal calculations to use as many digits as
  possible.  For all backends, accuracy could be improved by
  increasing the representational range and increasing the number of
  evaluation points generated when solving for decoding weights.

Figure 2:

  Again, it is likely that performance at the extremes of the
  representational range is responsible for the SpiNNaker backend's
  reduced accuracy, though we have not investigated this in detail.
  This benchmark also suggests that the reference and OpenCL backends
  have more variability than the Brainstorm and distilled backends.

@@

> Also, the whiskers in Figs. 1-4 seem to be only multiples of the box
> sizes, so plotting them does not add any information - it may be
> even misleading when not carefully reading the caption.

Thank you for bringing up this point!
Our description of the box plot was not quite correct
in the initial submission. We have rewritten this description
as follows:

  The box shows the median and interquartile range, while the whiskers
  extend to the farthest data point within 1.5 times the interquartile
  range; outliers are shown above and below the whiskers.

As noted in the revised captions, we have also now included the outliers.
We were initially concerned that outliers would make the rest of the
boxplot too small relative to the expanded axes caused by outliers.
However, we now feel that including all of the data makes these
boxplots more useful.

### 2015-09-14 paper/rebuttals.txt

Very few networks in Nengo have zero probes,
so there were some obvious opportunities to optimize
the reference backend for the special case
in which no probes exist. After implementing
two such optimizations, we were able to consistently
achieve identical performance with probes and without.
However, it was not our intention to perform
a detailed comparison of the effect of probes
on runtimes, and we feel that including Figure 7
(which only had a few sentences of text associated with it)
was more distracting than illuminating.
For these reasons, we have removed Figure 7 in this revision.

6. Other comments on the discussion or the conclusions.
-------------------------------------------------------

> As already mentioned for the Introduction, it would make the
> Discussion section much more balanced if the limitations of the
> approach would be discussed as well, together with some outlook to
> potential improvements or complementary approaches.

As previously mentioned, we added in a paragraph to the discussion
on the primary weakness of the approach.
This paragraph also includes a potential improvement:
collecting power consumption information (lines 416-422).

### 2015-09-14 paper/paper.tex
Final edits before submission

Prior work benchmarking neural simulators
and neuromorphic hardware has focused
on low-level neural performance.
For example, \citet{sharp2013}
showed that SpiNNaker can simulate
a recurrent network of leaky integrate-and-fire neurons
with similar firing rate and inter-spike intervals
as the NEST neural simulator,
but around six times faster.
\citet{stromatias2013} showed that
SpiNNaker's power consumption varies
between 15 and 37 Watts
(0.5--0.8 Watts per chip)
depending on the number of neurons
being simulated.
\citet{goodman2008brian} showed that
Brian simulated a randomly connected
network of 4000 leaky integrate-and-fire
twice as fast as an equivalent Matlab implementation,
but around three times slower than
a C implementation.
In all of these cases,
none of the networks
elicited activity that could be
directly related to experimentally recorded data
on a behavioral task.

@@

\paragraph{\texttt{Simulator}}
allows tests to be run with multiple backends.
As detailed in Section~\ref{Sec:Backend},
each backend must expose a simulator class
that accepts a network.
Every test uses this test fixture rather than
an actual class so that
the backend-specific simulator class is used
when the test is run.
Each backend's test suite loads
the tests defined in Nengo,
but replaces the implementation of
this fixture with their own fixture
returning that particular backend's simulator class.

@@

Unlike software backends,
considerable effort is taken
to translate a Nengo model into
something that can run on a SpiNNaker board.
Fortunately, SpiNNaker can be reprogrammed
as it is composed of a large collection
of chips, each with 18 ARM processing cores.
In particular, this allows SpiNNaker
to take advantage of Nengo's
encoding and decoding capabilities,
greatly reducing the amount of RAM needed
\citep{mundy2015}.
The SpiNNaker backends accomplishes this
by using decoded values to determine
changes to the input currents to each neuron,
rather than using purely
spike-based transmission.
However, neuromorphic hardware that
can only communicate through spikes
can be made to interact with Nengo
through explicit encoding and decoding processes
on the chip, as was done in \citealp{galluppi2012},
or by using Nengo on the host machine
to explicitly generate spike patterns
that are communicated to the device,
as was done in \citealp{choudhary2012}.
However, these methods may introduce
additional noise in the simulation,
resulting in inaccuracies.

@@

It should be noted that these test suites
are being run on the distilled, Brainstorm,
and SpiNNaker backends for the first time in this study.
In other words, these results are the first objective
interrogation of each backend's feature set.
In many cases, tests failed by backends
are tests of features recently added
to Nengo, such as stochastic processes
for injecting current noise.
As such, we expect compliance on all backends
to rise quickly as backend developers
implement these new features.
The OpenCL backend has
significantly higher compliance in large part
because it is developed by the same
group that develops the reference backend.
However, there are some notable features
missing from some backends,
such as learning through plasticity rules
applied to neuron-to-neuron connections,
and implementation differences,
such as one timestep delays on connections
with no synaptic filter,
that may remain even when backends
are brought up to date with
the reference implementation.
It is likely that tests will be rewritten
in the future to allow some implementation differences
if they do not affect simulation accuracy.

@@

Figure~\ref{fig:02} gives accuracy results
for the two-dimensional product model.
In this case, while all of the backends
perform well, the SpiNNaker backend
is less accurate than the other four backends.
Its performance, however, is still well within
acceptable ranges for the two-dimensional product model.
Again, it is likely that performance at the extremes
of the representational range
is responsible for the SpiNNaker backend's
reduced accuracy,
though we have not investigated this in detail.
This benchmark also suggests that
the reference and OpenCL backends
have more variability than other backends,
particularly the Brainstorm and distilled backends.

Figure~\ref{fig:03} gives accuracy results
for the controlled oscillator model.
The reference and OpenCL backends perform well here,
as do the distilled and Brainstorm backends.
The median accuracy of the SpiNNaker is
the same as the distilled and Brainstorm backends,
but there are a high proportion of model instances
with less accuracy than the median,
as compared to other backends.
In this example, differences in how each backend
implements synaptic filtering
are more pronounced than in previous examples,
as the recurrent connection is responsible
for the dynamics of the oscillation.
Relatively large variability in the
reference, OpenCL and SpiNNaker backends
suggests that their synaptic filtering implementations
should be examined for potential accuracy improvements.

@@

We thank Andrew Mundy for his help
running the SpiNNaker backend
and providing feedback on drafts of this paper.
We thank Jan Gosmann for the initial version
of the product benchmark models,
and for conceptualization and implementation
of the \texttt{analytics} and \texttt{analytics\_data}
fixtures.
We thank Xuan Choo for administering
the server on which the benchmarks were run,
Eric Hunsberger for help in running
the benchmarks on the OpenCL backend,
and James Bergstra for
implementing most of the OpenCL backend.
We thank the Brainstorm group
at Stanford University for making
their experimental hardware emulation backend
available to us.

>>>>

Prior work benchmarking neural simulators
and neuromorphic hardware has focused
on low-level neural performance.
For example, \citet{sharp2013}
showed that SpiNNaker can simulate
a recurrent network of leaky integrate-and-fire neurons
with similar firing rates and inter-spike intervals
as the NEST neural simulator,
but around six times faster.
\citet{stromatias2013} showed that
SpiNNaker's power consumption varies
between 15 and 37 Watts
(0.5--0.8 Watts per chip)
depending on the number of neurons
being simulated.
\citet{goodman2008brian} showed that
Brian simulated a randomly connected
network of 4000 leaky integrate-and-fire
twice as fast as an equivalent Matlab implementation,
but around three times slower than
a C implementation.
In all of these cases,
none of the networks
elicited activity that could be
directly related to experimentally recorded data
on a behavioral task.

@@

\paragraph{\texttt{Simulator}}
allows tests to be run with multiple backends.
As detailed in Section~\ref{Sec:Backend},
each backend must expose a simulator class
that accepts a network.
Every functional test uses this test fixture rather than
an actual class so that
the backend-specific simulator class is used
when the test is run.
Each backend's test suite loads
the tests defined in Nengo,
but replaces the implementation of
this fixture with their own fixture
returning that particular backend's simulator class.

@@

Unlike software backends,
considerable effort is taken
to translate a Nengo model into
something that can run on a SpiNNaker board.
Fortunately, SpiNNaker can be reprogrammed
as it is composed of a large collection
of chips, each with 18 ARM processing cores.
Notably, this allows SpiNNaker
to take advantage of Nengo's
encoding and decoding capabilities,
greatly reducing the amount of RAM needed
\citep{mundy2015}.
The SpiNNaker backend accomplishes this
by using decoded values to determine
changes to the input currents of each neuron,
rather than using purely
spike-based transmission.
However, neuromorphic hardware that
can only communicate through spikes
can be made to interact with Nengo
through explicit encoding and decoding processes
on the chip, as was done in \citet{galluppi2012},
or by using Nengo on the host machine
to explicitly generate spike patterns
that are communicated to the device,
as was done in \citet{choudhary2012}.
However, these methods may introduce
additional noise in the simulation,
resulting in inaccuracies.

@@

It should be noted that these test suites
are being run on the distilled, Brainstorm,
and SpiNNaker backends for the first time in this study.
In other words, these results are the first objective
interrogation of each backend's feature set.
In many cases, tests failed by backends
are tests of features recently added
to Nengo, such as stochastic processes
for injecting current noise.
As such, we expect compliance on all backends
to rise quickly as backend developers
implement these new features.
The OpenCL backend has
higher compliance in large part
because it is developed by the same
group that develops the reference backend.
However, there are some notable features
missing from some backends,
such as learning through plasticity rules
applied to neuron-to-neuron connections,
and implementation differences,
such as one timestep delays on connections
with no synaptic filter,
that may remain even when backends
are brought up to date with
the reference implementation.
It is likely that tests will be rewritten
in the future to allow some implementation differences
if they do not affect simulation accuracy.

@@

Figure~\ref{fig:02} gives accuracy results
for the two-dimensional product model.
In this case, while all of the backends
perform well, the SpiNNaker backend
is less accurate than the other four backends.
Its performance, however, is still well within
acceptable ranges for the two-dimensional product model.
Again, it is likely that performance at the extremes
of the representational range
is responsible for the SpiNNaker backend's
reduced accuracy,
though we have not investigated this in detail.
This benchmark also suggests that
the reference and OpenCL backends
have more variability than the Brainstorm and distilled backends.

Figure~\ref{fig:03} gives accuracy results
for the controlled oscillator model.
The reference and OpenCL backends perform well here,
as do the distilled and Brainstorm backends.
The median accuracy of the SpiNNaker is
the same as the distilled and Brainstorm backends,
but model instances with less accuracy than the median
perform poorly compared to other backends.
In this example, differences in how each backend
implements synaptic filtering
are more pronounced than in previous examples,
as the recurrent connection is responsible
for the dynamics of the oscillation.
Relatively large variability in the
reference, OpenCL and SpiNNaker backends
suggests that their synaptic filtering implementations
should be examined for potential accuracy improvements.

@@

We thank Andrew Mundy for his help
running the SpiNNaker backend
and providing feedback on drafts of this paper.
We thank Jan Gosmann for the initial version
of the product benchmark models,
and for conceptualization and implementation
of the \texttt{analytics} and \texttt{analytics\_data}
fixtures.
We thank Xuan Choo for administering
the server on which the benchmarks were run,
Eric Hunsberger for help in running
the benchmarks on the OpenCL backend,
and James Bergstra for
implementing most of the OpenCL backend.
We thank the Brainstorm group
at Stanford University for making
their experimental hardware emulation backend
available to us.
Finally, we thank our two reviewers for
their helpful feedback and recommendations.
